Life in the canopy: community trait assessments reveal substantial functional diversity among fern epiphytes

### 2019-12-30 ms/SI.rmd
Set margins of all figures to 0.2 in
also fixes cutoff portions of figs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)

@@

mpd_corr_plot <-
mpd_corr %>% 
  stretch(na.rm = TRUE) %>%
  mutate_at(c("x", "y"), forcats::fct_relevel, ... = order) %>% 
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r))), color = "white", size = 3) +
  scale_fill_scico(palette = "roma", breaks = c(-1, 1)) +
  labs(x = NULL, y = NULL, title = "a") +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  )

@@

mntd_corr_plot <-
  mntd_corr %>% 
  stretch(na.rm = TRUE) %>%
  mutate_at(c("x", "y"), forcats::fct_relevel, ... = order) %>% # Use same order as MPD
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r))), color = "white", size = 3) +
  scale_fill_scico(palette = "roma", breaks = c(-1, 1)) +
  labs(x = NULL, y = NULL, title = "b") +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  )

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE)

@@

mpd_corr_plot <-
mpd_corr %>% 
  stretch(na.rm = TRUE) %>%
  mutate_at(c("x", "y"), forcats::fct_relevel, ... = order) %>% 
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r))), color = "white", size = 3) +
  scale_fill_scico(palette = "roma", breaks = c(-1, 1)) +
  labs(x = NULL, y = NULL, title = "(a)") +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  )

@@

mntd_corr_plot <-
  mntd_corr %>% 
  stretch(na.rm = TRUE) %>%
  mutate_at(c("x", "y"), forcats::fct_relevel, ... = order) %>% # Use same order as MPD
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r))), color = "white", size = 3) +
  scale_fill_scico(palette = "roma", breaks = c(-1, 1)) +
  labs(x = NULL, y = NULL, title = "(b)") +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  )

@@

fig_s1 <- fig_s1 + plot_annotation(theme = theme(plot.margin = margin(
      0.2, 0.2, 0.2, 0.2, unit = "in")))
